draft_yma

### 2021-12-13 draft_yma.Rmd
first few model

```{r}
library(corrplot)
corrplot(cor(cdi_descriptive), type = "upper", diag = FALSE)
```

@@

>>>>

```{r}
library(corrplot)
cor(cdi_descriptive) %>% knitr::kable()

library(ggcorrplot)
library(ggstatsplot)
ggstatsplot::ggcorrmat(
  data = cdi,
  type = "parametric", # parametric for Pearson, nonparametric for Spearman's correlation
  colors = c("darkred", "white", "steelblue") # change default colors
)
```

@@

**we probably need to plot region as well? not sure**

## Model!

**Q: do we need more descriptive analysis, visualization? rate of crime for each state?**
**there's a few duplicated cty, but different area, maybe diff place then? not sure**
they can't be the same... otherwise we have to recalculate some stuff...
duplicated(cdi[,2:3])
cdi %>% filter(cty == "Baltimor")
cdi %>% filter(cty == "St._Loui")

#### Full model predictors ok?

included pop in addition to pop18, pop65. Do we need pop tho? Would pop18 and pop65 be enough already?

did not include cty, state, area, crimes, totalinc, totalinc (included pcincome), do we need to include any of those? for example, both totalinc and pcincome, area and pop_den

this model used `northeast` as the reference level for region

```{r}
cdi_model = cdi %>% select(-c(id,cty,state,area,crimes,totalinc))

# use 
full_fit = lm(crm_1000 ~ ., data = cdi_model)
summary(full_fit)
```

#### Backward

```{r}
fit_back = step(full_fit, direction='backward')
fit_back
```

crm_1000 ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model

#### forward

```{r}
fit_forward = step(full_fit, direction='forward')
fit_forward
```

crm_1000 ~ pop + pop18 + pop65 + hsgrad + bagrad + 
    poverty + unemp + pcincome + region + pdocs_1000 + pbeds_1000 + 
    density_pop, data = cdi_model

#### both

step-wise?

```{r}
fit_both = step(full_fit, direction='both')
fit_both
```

crm_1000 ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model
This gives back the same model as back

Some group forward again based on their first time step wise...not sure if we need to do that tho

### Test based procedures

#### Cp

I didn't include the full model here

**backward & both**

```{r}
# printing the 2 best models of each size. For example, the first two lines: print the best 2 models that have 2 variables (including intercept)
library(leaps)
Cp_b = leaps(x = model.matrix(fit_back)[,-1],
      y = cdi_model$crm_1000,
      nbest = 2,
      method = "Cp")
Cp_b

Cp_b %>% faraway::Cpplot()
```

size is the number of parameters in the model, Cp is Cp

The plot shows the model that satisfy the criteria, number indicates the number of parameters it included. in this case, the 1st to the last.

**forward**
```{r}
leaps(x = model.matrix(fit_forward)[,-1],
      y = cdi_model$crm_1000,
      nbest = 2,
      method = "Cp") %>% faraway::Cpplot()
```

So, multiple model satisfies the Cp criteria here.

#### Adj R2

**backward**
```{r}
adjr_b = leaps(x = model.matrix(fit_back)[,-1],
      y = cdi_model$crm_1000,
      nbest = 2,
      method = "adjr2")

adjr_b

adjr_b%>% 
  faraway::maxadjr(10)
```

**forward**
```{r}
leaps(x = model.matrix(fit_forward)[,-1],
      y = cdi_model$crm_1000,
      nbest = 2,
      method = "adjr2") %>% faraway::maxadjr(10)
```
